On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-01 docs/mvfits_paper/mvf.tex
Fix N->N+1 for S-W equation representation [22,23]

From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $KN$. This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.

>>>>

From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $K(N+1)$. This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.
